03_aggregation

### 2022-03-22 replication_data/rmd/02_format_and_clean.rmd
tsvs

dim(icb_wide_aligned_raw) #87710    85
```

@@

@@

@@

temp_wide <- icb_long_clean2 %>%
             dplyr::select(icb_survey_version, email_id, input_crisis,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
             dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
             dplyr::mutate(variable_normalized= variable_normalized %>% trimws() %>% tolower()) %>%
             dplyr::filter(variable_normalized %in% (c( 'sentence_events', drops ) %>% trimws() %>% tolower()) ) %>%
             dplyr::distinct() %>% 
             dplyr::left_join(full_tree %>% 
                       dplyr::rename(value_normalized=leaf)  %>% 
                       dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) 
                       )

@@

@@

>>>>

dim(icb_wide_aligned_raw) #87710    85

dim(unique(icb_wide_aligned_raw))
```

@@

Drop other instances where coder enters the same information twice

# YUGOSLAVIA I: CROATIA-SLOVENIA1 and YUGOSLAVIA I: CROATIA-SLOVENIA2 overlap for one coder, otherwise rows are identical

# z1 <- icb_wide_aligned %>% dplyr::filter(email_id == "expert1" & input_crisis=="YUGOSLAVIA I: CROATIA-SLOVENIA1" & sentence_number_int_aligned %in% c(37:50))
# z2 <- icb_wide_aligned %>% dplyr::filter(email_id == "expert1" & input_crisis=="YUGOSLAVIA I: CROATIA-SLOVENIA2" & sentence_number_int_aligned %in% c(37:50))
# z1==z2

icb_wide_aligned <- icb_wide_aligned %>% dplyr::filter(!(email_id == "expert1" & input_crisis=="YUGOSLAVIA I: CROATIA-SLOVENIA2" & sentence_number_int_aligned %in% c(37:50)))

# one coders entry for SAND WALL appear in duplicate
icb_wide_aligned <- icb_wide_aligned %>% dplyr::mutate(duplicate = duplicated(icb_wide_aligned))
icb_wide_aligned <- icb_wide_aligned %>% dplyr::filter(!(email_id == "undergrad49addaea" & input_crisis=="SAND WALL" & duplicate==TRUE)) %>% dplyr::select(-duplicate)

```{r}
# check for duplicates (should be empty)
icb_wide_aligned %>% dplyr::filter(icb_wide_aligned %>% dplyr::select(-input_crisis) %>% duplicated())
```

@@

```
```{r}
# Check that each entry has only one event_type entry (should be all false)
icb_long %>% dplyr::filter(variable=="event_type") %>% dplyr::select(email_crisis_sent_event) %>% duplicated() %>% table()
```

@@

# THIS IS WHERE I AM
# give every entry its own event_type var to control merging (avoid merging in details for actions that were 'thought about' or 'said')
# confirm that no email_crisis_sent_event have more than one event_type entry
icb_long_clean2 %>% dplyr::filter(variable_normalized == "event_type") %>% 
  dplyr::select("email_crisis_sent_event", "value_normalized") %>% 
  dplyr::rename(event_type=value_normalized) %>% dplyr::count(email_crisis_sent_event) %>% dplyr::filter(n>1)

icb_long_clean2 <- icb_long_clean2 %>% 
  dplyr::left_join(icb_long_clean2 %>% dplyr::filter(variable_normalized == "event_type") %>% 
                     dplyr::select("email_crisis_sent_event", "value_normalized") %>% 
                     dplyr::rename(event_type=value_normalized))

```{r}
temp_wide <- icb_long_clean2 %>%
             dplyr::select(icb_survey_version, email_id, input_crisis,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, event_type, variable_normalized, value_normalized) %>%
             dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
             dplyr::mutate(variable_normalized= variable_normalized %>% trimws() %>% tolower()) %>%
             dplyr::filter(variable_normalized %in% (c( 'sentence_events', drops ) %>% trimws() %>% tolower()) ) %>%
             dplyr::distinct() %>% 
             dplyr::left_join(full_tree %>% 
                       dplyr::rename(value_normalized=leaf, variable_normalized=leaf_var)  %>% 
                       dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>% 
                       dplyr::mutate(variable_normalized= variable_normalized %>% trimws() %>% tolower())
                       ) %>% 
  dplyr::select(-event_type) #no longer needed after merge

@@

# readr::write_tsv(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.tsv"))

@@

# readr::write_tsv(icb_wide_clean, paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.tsv"))

### 2022-03-22 replication_data/rmd/03_aggregation.Rmd

options(warn = -1) #Groups that have no values generate max errors
#This doesn't have this yet
#event_number_int,  event_number_int_condition
rex_paste <- function(x){ paste0(x  %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
temp_long <- 
  icb_long_clean %>% 
    #filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence )  %>% #for debugging
    dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, event_number_int_condition,variable_normalized, value_normalized) %>% 
    dplyr::filter(value_normalized!='' & !is.na(value_normalized)) %>%
    dplyr::group_by(crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
    dplyr::select(-event_number_int) %>%
    dplyr::distinct() %>%
    dplyr::mutate(
      email_id = email_id %>% as.factor(), 
      #crisno= crisno %>% as.factor(),
      #sentence_number_int_aligned= sentence_number_int_aligned %>% as.factor(),
      crisno_sentence_number_int_aligned= paste0(crisno, "_", sentence_number_int_aligned) %>% as.factor(), #make sure these are the only factors or it'll try to criss cross sentence number and crisno etc.
      section= section %>% as.character(),
      sentence= sentence %>% as.character(),
      variable_normalized= variable_normalized %>% as.factor()
    ) %>%
    dplyr::select(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
    distinct() %>%
    dplyr::group_by(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, 
             variable_normalized,.drop=FALSE) %>% 
      #This drop false means every coder gets a '' whether they filled in that variable or not #section, sentence going to have to ignore the sentence text for now
      #You'll get a warning about adding it as a group
      summarise(value_normalized=value_normalized %>% rex_paste() ) %>%
    #that will add in dead ones now we want to split them back out
    dplyr::mutate(value_normalized = value_normalized %>% stringr::str_replace_all(";;",";")) %>% 
    dplyr::mutate(value_normalized = strsplit(as.character(value_normalized), ";", fixed=T)) %>% 
    tidyr::unnest(value_normalized) %>%
    dplyr::distinct() %>%
    #add a confidence score for every token
    dplyr::mutate(confidence=ifelse(variable_normalized=='raterconfidence', value_normalized, NA)) %>%

    dplyr::mutate(confidence=confidence %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
    dplyr::mutate(confidence_expert= email_id %>% stringr::str_detect('expert') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%
    dplyr::mutate(confidence_undergrad= email_id %>% stringr::str_detect('undergrad') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%

>>>>

options(warn = -1) #Groups that have no values generate max errors
#This doesn't have this yet
#event_number_int,  event_number_int_condition
rex_paste <- function(x){ paste0(x  %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
temp_long_step1 <- 
  icb_long_clean %>% 
    #filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence )  %>% #for debugging
    dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, event_number_int_condition,variable_normalized, value_normalized) %>% 
    dplyr::filter(value_normalized!='' & !is.na(value_normalized)) %>%
    dplyr::group_by(crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
    dplyr::select(-event_number_int) %>%
    dplyr::distinct() %>%
    dplyr::mutate(
      email_id = email_id %>% as.factor(), 
      #crisno= crisno %>% as.factor(),
      #sentence_number_int_aligned= sentence_number_int_aligned %>% as.factor(),
      crisno_sentence_number_int_aligned= paste0(crisno, "_", sentence_number_int_aligned) %>% as.factor(), #make sure these are the only factors or it'll try to criss cross sentence number and crisno etc.
      section= section %>% as.character(),
      sentence= sentence %>% as.character(),
      variable_normalized= variable_normalized %>% as.factor()
    )

temp_long_step2 <- temp_long_step1 %>%
    dplyr::select(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
    distinct() %>%
    dplyr::group_by(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, 
             variable_normalized,.drop=FALSE) %>% 
      #This drop false means every coder gets a '' whether they filled in that variable or not #section, sentence going to have to ignore the sentence text for now
      #You'll get a warning about adding it as a group
      summarise(value_normalized=value_normalized %>% rex_paste() ) %>%
    #that will add in dead ones now we want to split them back out
    dplyr::mutate(value_normalized = value_normalized %>% stringr::str_replace_all(";;",";")) %>% 
    dplyr::mutate(value_normalized = strsplit(as.character(value_normalized), ";", fixed=T)) %>% 
    tidyr::unnest(value_normalized) %>%
    dplyr::distinct() %>%
    #add a confidence score for every token
    dplyr::mutate(confidence=ifelse(variable_normalized=='raterconfidence', value_normalized, NA)) %>%
    dplyr::mutate(confidence=confidence %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
    dplyr::mutate(confidence_expert= email_id %>% stringr::str_detect('expert') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%
    dplyr::mutate(confidence_undergrad= email_id %>% stringr::str_detect('undergrad') %>% ifelse(confidence,NA) %>% max(na.rm=T) )

```{r}
temp_long <- temp_long_step2 %>%
